`It Is Unbearable To Breath Here': Air Quality, Open Incineration, And Misinformation In Blantyre, Malawi

### 2023-05-19 manuscript/manuscript-qech-air-quality-tilley.qmd
Rename file

(TODO: REPLACE screenshot with actual data)

```{r}
#| label: tbl-who-targets
#| tbl-cap: Particulate matter targets from [@worldhealthorganization2021who]

knitr::include_graphics(here::here("manuscript/img/image-replace-table.png"))

>>>>

```{r}
#| label: tbl-who-targets
#| tbl-cap: Recommended long- and short-term AQG (Air Quality Guidelines) levels and interim targets.

who_target_tidy |>
  pivot_wider(names_from = "interim_target",
              values_from = "concentration") |>
  filter(str_detect(pollutant, "PM")) |>
  relocate(AQG_level, .after = "4") |>
  group_by(averaging_time) |>
  # prepare table
  gt(rowname_col = "pollutant") |>
  tab_spanner(label = md("**Interim target**"), columns = `1`:`4`) |>
  cols_label(
    averaging_time = "Averaging time",
    AQG_level = "AQG level"
  ) |>
  fmt_number(columns = `1`:AQG_level, decimals = 1) |>
  tab_style(
    locations = cells_column_labels(),
    style = list(cell_text(weight = "bold"))
  ) |>
  tab_style(locations = cells_row_groups(),
            style = list(cell_text(weight = "bold"))) |>
  text_transform(locations = cells_stub(),
                 fn = function(x) { 
                   x |> 
                     str_replace_all("2.5", "$_{2.5}$") |> 
                     str_replace_all("3", "$_{3}$") |> 
                     str_replace_all("10", "$_{10}$") }
                 ) |> 
  tab_footnote(
    footnote = "99th percentile (i.e. 3-4 exceedance days per year).",
    locations = cells_row_groups(group = "24-hour")
  )

### 2023-05-19 manuscript/manuscript-qech-air-quality-tilley.tex
Rename file

\begin{keyword}
    waste management \sep healthcare waste \sep trash burning \sep air
quality \sep Malawi \sep 
    urbanisation
\end{keyword}
\end{frontmatter}
    \ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[interior hidden, boxrule=0pt, enhanced, sharp corners, breakable, frame hidden, borderline west={3pt}{0pt}{shadecolor}]}{\end{tcolorbox}}\fi

@@

{\centering \includegraphics{manuscript_files/figure-pdf/fig-24-hour-average-1.pdf}

@@

{\centering \includegraphics{manuscript_files/figure-pdf/fig-pm-ratios-1.pdf}

@@

{\centering \includegraphics{manuscript_files/figure-pdf/fig-percent-exposure-1.pdf}

@@

{\centering \includegraphics{manuscript_files/figure-pdf/fig-five-minute-intervals-1.pdf}

>>>>

\begin{keyword}
    waste management \sep healthcare waste \sep trash burning \sep air
quality \sep Malawi \sep 
    urbanisation
\end{keyword}
\end{frontmatter}
    \ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[frame hidden, sharp corners, interior hidden, enhanced, boxrule=0pt, borderline west={3pt}{0pt}{shadecolor}, breakable]}{\end{tcolorbox}}\fi

@@

{\centering \includegraphics{manuscript-qech-air-quality-tilley_files/figure-pdf/fig-24-hour-average-1.pdf}

@@

{\centering \includegraphics{manuscript-qech-air-quality-tilley_files/figure-pdf/fig-pm-ratios-1.pdf}

@@

{\centering \includegraphics{manuscript-qech-air-quality-tilley_files/figure-pdf/fig-percent-exposure-1.pdf}

@@

{\centering \includegraphics{manuscript-qech-air-quality-tilley_files/figure-pdf/fig-five-minute-intervals-1.pdf}
